\chapter{Introduction}
Every program computes on either sensitive data or non-sensitive data. Sensitive is any data that can be used to 
identify the user or any private user information, such as photos, International Mobile Equipment Identity (IMEI) 
nd biometric data. Non-sensitive data is any dynamic information that do not identify the user, oftenly this kind 
of information if public or shared, such as application source code.

In an application, data follows a specific flow, first it is acquired from data sources and sent to data 
sinks \citep{mccabe2003network}. Data sources, in the context of mobile and IoT devices, are defined as method 
calls that read data from shared resources such as phone calls, screenshots, sensor polling data from ambient, 
device identification numbers \citep{rasthofer2014machine}. Data sinks are methods calls that have at least one 
argument, this argument is non-constant data from the source code \citep{rasthofer2014machine}. The data sink can be
an interface to the user or system API for communication to other devices or store data \citep{viet2010specifying}.

Dynamic Flow Enforcement are techniques that tracks and enforces information flow during the application runtime. 
These methods relies on Taint Analysis to track possible sensitive data flow to untrusted sinks. Taint Analysis 
marks every sensitive data gathered from a source and every other variable that inherit any operation 
from the tainted data, in the end, if any tainted variable is accessed by a sink method, the information has 
leaked and the analysis gives a detailed path through which the data passed. During the tracking, there are 
different methods to enforce in runtime that the data will not leak, \cite{fernandes2016flowfence} uses 
virtualization to guarantee that the data will only operate in the controlled environment and \cite{sun2017data} 
declassifying information before it is computed in trusted methods or if reach a trusted API.

Static Flow Enforcement starts by creating abstract models of the application code to provide a simpler 
representation \citep{myers1999jflow}, using frameworks like Soot \citep{vallee2000optimizing}. Then, this model 
will be used in control-flow, data-flow and points-to analysis to observe the application control, data sequence 
and compute static abstractions for variables \cite{li2017static}. These methods are implemented and used in 
DroidSafe \cite{gordon2015information}. JFlow \cite{myers1999jflow} inserts statically checked and secured code 
when the application computes on sensitive data.

Both Static and Dynamic Flow Enforcement techniques require information of which methods is a source of sensitive 
data and which is a data sink. This is used to identify if a sink method is truly leaking sensitive data or not. So,
lists containing sources and sinks of sensitive data are hand created, but this solution is impractical considering 
a huge API like the Android API \cite{rasthofer2014machine}.

Considering that issue, Rasthofer et al. \cite{rasthofer2014machine} proposed to use machine learning to 
automatically create a categorized list of sources and sinks methods to be used in Flow Enforcement techniques.
The list consists in methods classified into Flow Classes and Android Method Categories. The Flow Classes are 
source of sensitive data, or just source, and sink of data, but also, the method can be neither source or sink. For 
Android Methods Categories, there are 12 different classes: account, Bluetooth, browser, calendar, contact, 
database, file, network, NFC, settings, sync, a unique identifier, and no category if the method does not belong to 
any of the previous.

The authors shortly compared Decision Trees and Naive Bayes with the SVM and choosed to use SVM to create the 
categorized list of sources and sinks, as SVM showed to be more precise in categorize the Android methods. 

To classify, the authors utilize features extracted from the methods, like the method name, if the method has 
parameters, the return value type, parameter type, if the parameter is an interface, method modifiers, class 
modifiers, class name, if the method returns a value from another source method, if one parameter flows into a sink 
method, if a method parameters flows into a abstract sink and the method required permission. 

To categorize the methods, were used features like class name, method invocation, body contents, parameter type and 
return value type. After that, the methods list is generated containing if it is a sink, source and the method 
category.
